Blum axioms and nondeterministic computation of functions

### 2016-04-20 paper.tex
paper.tex: Simplify criticism of Hopcroft and Ullman's definition.

\begin{proposition}
    The function partial $f: \Sigma^* \times \Sigma^* \to \{0, 1\}$ defined by
    \begin{equation*}
        f(w, x) = \begin{cases}
            1, & \text{if the machine $w$ does not halt on $x$.} \\
            \text{undefined}, &\text{if $w$ never halts on $x$.}
        \end{cases}
    \end{equation*}
    is not computable,
    but can be computed by a nondeterministic Turing machine under
    Hopcroft and Ullman's definition.
\end{proposition}

\begin{proof}
    If $f$ were computable,
    we could take a deterministic machine $M$ that computes it
    and replacing halting
    (which only happen if $M$ would return $1$)
    with acceptance.
    This new machine would recognize the complement (under $\{0, 1\}^*$)
    of the halting problem,
    a contradiction.

    But $f$ can be computed under Hopcroft and Ullman's definition as follows:
    on input $(w, x)$,
    create two branches of computation.
    On the first, write $1$ on the tape and halt.
    On the second, simulate the universal Turing machine $U$ in the input,
    and if $U$ halts, write $0$ on the tape and halt too.

    If $w$ halts on $x$,
    there will be two halting branches of computation,
    each writing a different value in the tape,
    so, by definition, the function is not defined on this input.
    If $w$ never halts,
    then only the first branch will halt
    (and with $1$ written on the tape),
    so the function is defined on this input and its value is $1$.

    Thus, under Hopcroft and Ullman's definition,
    this machine computes the noncomputable function $f$,
\end{proof}

Therefore,
using Hopcroft and Ullman's definition,
we could enumerate functions that are not computable;
so, the image of the corresponding ``Gödel numbering''
would include noncomputable functions.

>>>>

\begin{proposition}
    The function partial $f: \Sigma^* \times \Sigma^* \to \{0, 1\}$ defined by
    \begin{equation*}
        f(w, x) = \begin{cases}
            1, & \text{if the machine $w$ does not halt on $x$.} \\
            \text{undefined}, &\text{if $w$ never halts on $x$.}
        \end{cases}
    \end{equation*}
    Can be computed by a nondeterministic Turing machine under
    Hopcroft and Ullman's definition.
\end{proposition}

\begin{proof}
    On input $(w, x)$,
    create two branches of computation.
    On the first, write $1$ on the tape and halt.
    On the second, simulate the universal Turing machine $U$ in the input,
    and if $U$ halts, write $0$ on the tape and halt too.

    If $w$ halts on $x$,
    there will be two halting branches of computation,
    each writing a different value in the tape,
    so, by definition, the function is not defined on this input.
    If $w$ never halts,
    then only the first branch will halt
    (and with $1$ written on the tape),
    so the function is defined on this input and its value is $1$.
\end{proof}

Therefore,
using Hopcroft and Ullman's definition,
we can compute some noncomputable functions,
violating the requirement~\ref{surjectiveness} of Gödel numberings.
